### 2025-09-22 paper/sec/evaluation.tex
first pass result

>>>>

\subsection{Results}
In this section, we present the experimental results.
Overall, the system produced a valid fluid expression in 74.9\% of the cases (S.D. 3\%).
Figure~\ref{fig:success_rate_by_category} illustrates the success rate for each category.

The system achieved performance above 70\% in comparison, data retrieval, and min/max search tasks.
In contrast, accuracy decreased significantly in expressions requiring differences (20\%) and in ranking tasks (50\%).

Figure~\ref{fig:success_rate_by_category_count} reports the success rate as a function of the number of categories assigned to each expression.
Fluid instructions combining multiple operations were associated with multiple categories.
Results show that the success rate was 75\% for simple expressions (one category), increased to 85\% for two categories,
and dropped to 58\% when three categories were involved.
